Alex's Notes and Text Fragments for the JSS Manuscript

### 2023-08-15 paper/article.Rmd
increase label size and show_omitted points

autoplot(rsmp_buffer, size = 0.8, task = task, fold_id = 1)
```

@@

autoplot(rsmp_buffer,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

autoplot(rsmp_disc, size = 0.8, task = task, fold_id = 1)
```

@@

autoplot(rsmp_disc,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

autoplot(rsmp_block_random, size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE)
```

@@

autoplot(rsmp_block_random,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

autoplot(rsmp_block_systematic, size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE)
```

@@

autoplot(rsmp_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

>>>>

autoplot(rsmp_buffer, size = 0.8, task = task, fold_id = 1, show_omitted = TRUE)
```

@@

autoplot(rsmp_buffer,
  size = 0.8, task = task, fold_id = 1, show_omitted = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

autoplot(rsmp_disc, size = 0.8, task = task, fold_id = 1, show_omitted = TRUE)
```

@@

autoplot(rsmp_disc,
  size = 0.8, task = task, fold_id = 1, show_omitted = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

autoplot(rsmp_block_random, size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE, label_size = 4)
```

@@

autoplot(rsmp_block_random,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE, label_size = 4) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```

@@

autoplot(rsmp_block_systematic, size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE, label_size = 4)
```

@@

autoplot(rsmp_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE, label_size = 4) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02)) +
  ggplot2::theme(text = ggplot2::element_text(size = 16),
    plot.title = ggtext::element_textbox(size = 13,
      r = ggplot2::unit(7, "pt"),
      height = ggplot2::unit(0.46, "inch"), linewidth = 0.8)) +
  ggplot2::guides(colour = ggplot2::guide_legend(override.aes = list(size = 1.5)))
```
